Scikit-learn: machine learning without learning the machinery

### 2014-11-06 article.tex
ILPS -> ISLA (Intelligent Systems Lab Amsterdam)
grammar fixes
GPGPU, again; address Gaël's comments

Machine learning is a very active field of research, with promising
trends such as deep learning, harnessing GPUs or distributed computing
for extra computational power, or extending to new platforms, such as
Android or iOS-based embedded devises. However, as scikit-learn's purpose
is to provided tried-and-true, mostly turn-key, predictive tools, we have
to walk the fine line between supporting powerful techniques and
utilizing our limited project cycles on proven technologies. For
instance, deep neural networks are an emerging tool with a huge
potential, but are still in flux and hard to use without significant expertise.

Similarly, GPGPU technology is promising, but still poses user-level problems.
While OpenCL largely hides the incompatibility of GPUs and other compute devices
at the source code level \cite{stone2010opencl}, it does not guarantee performance portability
and requires the installation of device-specific drivers.
PyOpenCL \cite{klockner2012pycuda} may alleviate the former problem and communicates
with NumPy, making it an obvious starting point for experimentation
in the direction of GPU-enabled scikit-learn. Theano \cite{bergstra2010theano} has
shown the feasibility of programming GPU-powered neural nets in Python.

>>>>

Machine learning is a very active field of research, with promising
trends such as deep learning, harnessing GPUs or distributed computing
for extra computational power, or extending to new platforms, such as
Android or iOS-based embedded devises. However, as scikit-learn's purpose
is to provided tried-and-true, mostly turn-key, predictive tools, we have
to walk the fine line between supporting powerful techniques and
utilizing our limited project cycles on proven technologies. For
instance, deep neural networks are an emerging tool with a huge
potential, but are still in flux and hard to use without significant expertise.
Similarly, GPGPU technology is promising, but not ready for non-expert use.
The HPC community and industry have largely achieved source-level compatibility with OpenCL
\cite{stone2010opencl},
but still need to solve the problems of performance portability and cross-platform driver support.
